Multisensor Architecture for an Intersection Management System

### 2019-01-28 ch3-arch_sys.tex
Figures reordered and format improved in sections 2.3.4

\todo{Design Considerations}

@@

This block takes as input a message of type laser\_pol\_msg for converting it into cartesian coordinates referenced to global system. For this reason, it also takes a laser\_cfg parameter to include laser position information in the conversion. Output message contains a set of x, y points obtained from the following equations:

@@

\item[laser\_cart\_merge] \hfill

@@

This block takes as input messages of type laser\_cart\_msg coming from different sensors and merges them into a single message, based on a sampling period $T$.

@@

\item[virtual\_sensor\_merge] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/vs_merge.pdf}
\caption{virtual\_sensor\_merge}
\label{virtual_sensor_merge}
\end{figure}

This block is intended to take as inputs different messages of type vs\_occ\_msg and merging them to increase the reliabilty of detection. First, a moving average is calculated over each input to reduce the effect of false positives or false negatives in a single frame. After this, the inputs are merged by a defined method like average, weighted average, maximum or minimum. Then, a new vs\_occ\_msg message is dispatched as output.

@@

\item[virtual\_sensor\_to\_flow\_rate] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/vs2flow.pdf}
\caption{virtual\_sensor\_to\_flow\_rate}
\label{virtual_sensor_to_flow_status}
\end{figure}

@@

@@

\item[flow\_rate\_to\_flow\_status] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/flow2status.pdf}
\caption{flow\_rate\_to\_flow\_status}
\label{flow_rate_to_flow_status}
\end{figure}

@@

@@

\item[laser\_publisher] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/laser_publisher.pdf}
\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
\caption{laser\_publisher and camera\_publisher}
\label{sensors_publishers}
\end{figure}

@@

>>>>

%\todo{Design Considerations}

As the implementation of a full Intersection Management System is a joint effort among different fields of engineering (Hardware, software, IT, civl) and even non-engineering areas, The two main features chosen for this proposal are scalability and modularity. Scalability is desired in the cases where an initial deployment needs to expand or increase its complexity in any of its areas, for example, new communication approaches, add new sensors or hardware, develop new features or policies, etc. Modularity allows that the internal blocks of system could be modified, exchanged or enhanced without disturbing the overall function of the deployment. This criteria is achieved with the four proposed elements of this architecture: communication scheme, data model, information structure and processing blocks.

@@

This block takes as input a message of type laser\_pol\_msg for converting it into cartesian coordinates referenced to global system. For this reason, it also takes a laser\_cfg parameter to include laser position information in the conversion. Output message contains a set of x, y points, referenced to a global coordinate system. This output is obtained from the following equations:

@@

\hfill
\item[laser\_cart\_merge] \hfill

@@

This block takes as input messages of type laser\_cart\_msg coming from different sensors and merges them into a single message, based on a sampling period $T$. The objective of this stage is to set a common time-frame and synchronize all the messages to feed to the next blocks.

@@

\hfill

\item[virtual\_sensor\_merge] \hfill
This block is intended to take as inputs different messages of type vs\_occ\_msg and merging them to increase the reliabilty of detection. First, a moving average is calculated over each input to reduce the effect of false positives or false negatives in a single frame. After this, the inputs are merged by a defined method like average, weighted average, maximum or minimum. Then, a new vs\_occ\_msg message is dispatched as output.
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/vs_merge.pdf}
\caption{virtual\_sensor\_merge}
\label{virtual_sensor_merge}
\end{figure}

@@

\item[virtual\_sensor\_to\_flow\_rate] \hfill

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/vs2flow.pdf}
\caption{virtual\_sensor\_to\_flow\_rate}
\label{virtual_sensor_to_flow_status}
\end{figure}

@@

\hfill

\item[flow\_rate\_to\_flow\_status] \hfill

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/flow2status.pdf}
\caption{flow\_rate\_to\_flow\_status}
\label{flow_rate_to_flow_status}
\end{figure}

@@

\item[laser\_publisher] \hfill

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/laser_publisher.pdf}
\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
\caption{laser\_publisher and camera\_publisher}
\label{sensors_publishers}
\end{figure}
